### 2021-05-01 notes/penetration_argument/penetration_argument.tex
adds Zahn penetration argument; works through all of it for erf.

We next assume that the temperature and velocity are highly correlated in the overshooting convective motions (upflows).
This allows us to describe the horizontal nature of all fields in upflows using a function $h(x,y)$ so that
\begin{equation}
w(x,y,z) = W(z) h(x,y)
\qquad
T'(x,y,z) = \delta T(z) h(x,y),
\end{equation}
where $T'$ are the temperature fluctuations away from the mean.
By continuity and by our above definition of the convective flux, we have
\begin{equation}
\overline{h} = 0,
\qquad
\overline{h^2} = f.
\end{equation}

>>>>

We next assume that the temperature and velocity are highly correlated in the overshooting convective motions (upflows).
This allows us to describe the horizontal nature of all fields in upflows using a function $h(x,y)$ so that
\begin{equation}
w(x,y,z) = W(z) h(x,y)
\qquad
T'(x,y,z) = \delta T(z) h(x,y),
\end{equation}
where $T'$ are the temperature fluctuations away from the mean.
By continuity and by our above definition of the convective flux, we have
\begin{equation}
\overline{h} = 0,
\qquad
\overline{h^2} = f.
\end{equation}
Furthermore, as in \citet{zahn1991}, $h$ is normalized so that its mean square averages to zero over the area where $h > 0$,
\begin{equation}
\overline{h^2 \mu(x,y)} = 1,
\end{equation}
where $\mu(x,y) = (1 + h/|h|)/2$, which is 1 when $h > 0$ and 0 when $h \leq 0$.

Per the momentum equation, the deceleration of plumes in the penetration zone is described by buoyancy breaking,
\begin{equation}
\frac{d w^2}{dz} = \alpha g T'.
\end{equation}
Multiplying by $h$ (to preserve the LHS) and taking a horizontal average, we get
\begin{equation}
\frac{\overline{h^3}}{\alpha g f}d W^2 = \delta T dz.
\end{equation}
After elimination of $\delta T$ with the formula for $F_{\rm{conv}}$, we integrate
\begin{equation}
\frac{\overline{h^3}}{3 \alpha g}\int_{W_0}^0 dW^3 = \int_{L_{\rm{cz}}}^{L_{\rm{cz}} + L_p} F_{\rm{conv}}\, dz,
\label{eqn:buoyancy_integral}
\end{equation}
assuming that the velocity drops to roughly $W = 0$ at $z = L_{\rm{cz}} + L_p$, where $L_{\rm{cz}}$ is the height where $\grad_{\rm{rad}} = \grad_{\rm{ad}}$.

At this point we will consider two cases:
\begin{enumerate}
\item The ``erf'' simulations, where we assume that $F_{\rm{conv}}$ jumps from a value of $F_0$ in the CZ to a value of $-F_0/\mathcal{P}$ in the PZ.
In this case, integration of a constant straightforwardly returns
\begin{equation}
L_p = \frac{\overline{h^3} W_0^3}{3\alpha g F_0}\mathcal{P}.
\end{equation}
\item The ``linear'' simulations, where we assume that $F_{\rm{conv}}$ decreases from a value of 0 at $L_{\rm{cz}}$ linearly, so $F(z > L_{\rm{cz}}) = -|\partial_z F_0|(z - L_{\rm{cz}})$.
We set $|\partial_z F_0| \sim \mathcal{P}^{-1}$ in these simulations.
In this case, integration yields
\begin{equation}
L_p = \left(\frac{2\overline{h^3} W_0^3}{3\alpha g|\partial_z F_0|}\right)^{1/2} \propto \sqrt{\mathcal{P}}.
\end{equation}
This is more directly the case mentioned by Zahn.
\end{enumerate}

Following a step further, we now adopt the assumption of MLT that the CZ flux is described by
\begin{equation}
F_{0} = \mathcal{F} W^3.
\end{equation}
The difficulty is in in determining the value of $\mathcal{F}$.
To achieve this, we return to Eqn.~\ref{eqn:buoyancy_integral} and integrate over the relevant length scale in the CZ (for the Boussinesq case, this is just the depth of the CZ),
\begin{equation}
\frac{\overline{h_{\rm{cz}}^3}}{3 \alpha g}\int_0^{W_0} dW^3 = \int_{0}^{L_{\rm{cz}}} F_0\, dz
\Rightarrow
F_0 = \frac{\overline{h_{\rm{cz}}^3} W_0^3}{3 \alpha g L_{\rm{cz}}},
\end{equation}
where above I have performed the integral for the ``erf'' case and assumed a constant $F_0$ in the CZ (I should be more careful about this, because internal heating, and my length scale is slightly off).
Plugging this expression for $F_0$ into the erf expression for $L_p$, we retrieve
\begin{equation}
\frac{L_p}{L_{\rm{cz}}} = \frac{\overline{h^3}}{\overline{h_{\rm{cz}}^3}} \mathcal{P},
\end{equation}
and we see that the penetration depth depends only on $\mathcal{P}$ and the horizontal extent of the upflows in the CZ compared to the PZ.
We expect the latter of these factors to be a weak function of things like the stiffness or the Reynolds number.
In the simulations I have thusfar conducted, I think I have found that the average filling factor $f$ of the flows decreases as you move upwards in the CZ (from something like 0.6 to 0.4); in the PZ it quickly returns to 0.5, and it stays 0.5 in the RZ (where waves dominate, and that makes sense).
However, I did these calculations using a pure filling factor calculation (``what fraction of the horizontal volume is filled with an upflow?''); I think a better algorithm which attempts to determine where the convective plumes are would be ideal.
Regardless, naively I think that $\overline{h^3} \approx f^{3/2}$ is probably a fine first assumption.
By that assumption, with the above numbers I quoted ($f_{\rm{cz}} \approx 0.6$ and $f_{\rm{pz}} \approx 0.4$), we get
\begin{equation}
\frac{L_p}{L_{\rm{cz}}} \approx \frac{f_{\rm{pz}}^{3/2}}{f_{\rm{cz}}^{3/2}}\mathcal{P} \approx 0.54 \mathcal{P}.
\end{equation}
This is strikingly close to what we are seeing in these simulations.
